---
title: "Benthamiana1"
author: "Sanford"
date: "12/30/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Bioassay data from **Benthamiana** project


```{r, echo=FALSE}
library(dplyr)
library(emmeans)
#GETTING IN THE DATA
# bioassayd<-read.csv("benthamianabioassay.csv",stringsAsFactors=T)
bioassaymod<-read.csv("benthamianabioassay_formodel.csv",stringsAsFactors=T)
#bioassayd
#bioassay9<-subset(bioassayd, TREAT!="_4077")
bioassay9<- droplevels(bioassayd[!bioassayd$TREAT == "_4077",])
str(bioassay9)
#bioassay9
 #summary(bioassayd)
 summary(bioassay9)  
 #ANOVAS COMPARING EMIGRATION AMONG TREATMENTS
 anova.first <-aov(X20~TREAT, data=bioassay9)# X10, X20 ... DIFFERENT TIMES
  summary(anova.first)
  #TukeyHSD(anova.first,  ordered = FALSE, conf.level = 0.95)

boxplot(X20~TREAT,data=bioassay9, las=2)
 contrast1 = c(1,1,1,1,1,0,0,0,-5)
 contrast2 = c(0,0,0,0,0,0,1,0,-1)
 contrast3 = c(1,1,1,1,1,1,1,-7,1)
 contrast4 = c(0,0,0,-1,0,0,0,0,1)
 contrasts(bioassay9$TREAT) = cbind(contrast1,contrast2,contrast3,contrast4)
#str(bioassay9)


#contrasts(bioassay9$TREAT)
 anova.second <-aov(X20~TREAT, data=bioassay9)
 summary.lm(anova.second)
 
 levels(bioassay9$TREAT)
```

## Treatments in order
__4050, _3648, 3705, 3861, 3879, Agro, control, paper, PLRVwild

## Contrast coefficients (revise based on script)
 contrast1 = c(1,1,1,1,1,0,0,0,-5)\
 contrast2 = c(0,0,0,0,0,0,1,0,-1)\
 contrast3 = c(1,1,1,1,1,1,1,-7,1)\
 contrast4 = c(0,0,0,-1,0,0,0,0,1)\
```{r, include=TRUE}
# EMIGRATION MODEL

str(bioassaymod)
#plot(bioassaymod$Time, bioassaymod$Emigrating, xlab = "seconds", ylab= "number emigrating/30")
#title("Scatter Plot of Emigration by Time")

attach (bioassaymod)
#bioassaymod
plot(Time,Remaining,  col = TREAT, pch = 1, xlab = "seconds", ylab= "number Remaining/30",xlim = c(0,75))
title("Scatter Plot of Emigration by Time")
legend("topright",c("__4050", "_3648", "3705", "3861", "3879", "Agro", "control", "paper", "PLRVwild"), col = 1:9, pch=1)

emmod<-lm(log(Remaining+0.1)~Time)
summary(emmod)

  
factor<-emmod$coefficients["Time"]
factor
coeff<-exp(emmod$coefficients["(Intercept)"])
coeff
factor<-round(factor,3)
coeff<-round(coeff,3)
fit_eq=paste("y=",coeff,"exp(",factor,"x)")
text(25,29,fit_eq)
curve(coeff*exp(factor*x),0,60,add=TRUE,col ="blue")

```
 
# second try
```{r, include=TRUE}
bioassaymod2<-data.frame(bioassaymod, group = TREAT)
#bioassaymod2
bioassaymodwt<-subset(bioassaymod2, group=="PLRVwild")
#bioassaymodpaper

attach (bioassaymodwt)
#bioassaymod
plot(Time,Remaining,  col = TREAT, pch = 1, xlab = "seconds", ylab= "number Remaining/30",xlim = c(0,75))
title("Scatter Plot of Emigration by Time")
legend("topright",c("__4050", "_3648", "3705", "3861", "3879", "Agro", "control", "paper", "PLRVwild"), col = 1:9, pch=1)

emmod<-lm(log(Remaining+0.1)~Time)
summary(emmod)

factor<-emmod$coefficients["Time"]
factor
coeff<-exp(emmod$coefficients["(Intercept)"])
coeff
factor<-round(factor,3)
coeff<-round(coeff,3)
fit_eq=paste("y=",coeff,"exp(",factor,"x)")
text(25,29,fit_eq)
curve(coeff*exp(factor*x),0,60,add=TRUE,col ="blue")

```
 
# NOTES\
MADE PROGRESS FITTING THE EMIGRATION DATA TO A MODEL AND PLOTTING. MODEL NEEDS WORK. NEED TO GET SOME ESTIMATE OF THE VARIANCE AROUND THE INTERCEPT AND SLOPE AND A WAY TO COMPARE THE LINES AMONG TREATMENTS. THE MODEL WORKS WELL FOR NUMBER OF SUBJECTS REMAINING, BUT WHEN I TRY TO WRITE FOR NUMBER EMIGRATING, SOMETHING DOESN'T WORK. MODEL BILL USED IS $N$ = $Rm$ × (1-e^–$\beta t$^), AND THAT IS NOT WHAT I'M USING, YET. I HOPE I CAN USE THIS BASIC CODE BUT MAYBE NOT.
 

 